### 2021-12-10 documentos/pce.tex
dandole

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The trace preserving
property is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving property is required for the process $\mcE$ to be deterministic, \ie{} $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho\in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local feature of quantum theory. A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert), \ \ \Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
decimos que es una matriz de densidad} \ddnote{$\Delta$ no es hermítico, sin embargo la definición de positividad-semidefinida se extiende a la parte hermítica por convención, revisé y en ningún libro mencionan la hermiticidad en este punto. Sin embargo esos casos no son relevantes en este contexto por supuesto}. In the other hand, a map is completely positive if
 $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
between the system and an ancilla with Hilbert space $\hilbert_k$. This ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators. The trace preserving is automatically
fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.
\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}

@@

Furthermore, quantum channels enjoy the well-known \textit{Kraus representation} (or
operator-sum representation) which reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{}
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition). In fact, a linear operation is completely positive if and only
if it has a Kraus representation~\cite{Kraus1983}. The minimum number of Kraus operators $K_i$ needed to represent the channel is called \textit{Kraus rank}. 
%
It can be seen from Kraus decomposition that quantum channels preserve
hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular in this work we use bases consisting in the so-called \textit{Pauli strings}, defined as 
\begin{equation}
\sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
\label{eq:pauli_strings}
\end{equation}
where $N$ is the number of two-level particles (\aka{} qubits), $\alpha_i=0,1,2,3$ and $\sigma_0:=\one$, $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal in $\mcB(\hilbert)$. Also notice that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
%
$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$
%

>>>>

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. Linearity is needed to
map every convex combination of density matrices into a convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving property is required for the process $\mcE$ to be deterministic, \ie{} $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho\in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local feature of quantum theory. A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert), \ \ \Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
decimos que es una matriz de densidad} \ddnote{$\Delta$ no es hermítico, sin embargo la definición de positividad-semidefinida se extiende a la parte hermítica por convención, revisé y en ningún libro mencionan la hermiticidad en este punto. Sin embargo esos casos no son relevantes en este contexto por supuesto}. In the other hand, a map is completely positive if
 $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
between the system and an ancilla with Hilbert space $\hilbert_k$. This ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators. The trace preserving is automatically
fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.
\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}

@@

Furthermore, quantum channels enjoy the well-known \textit{Kraus representation} (or
operator-sum representation) which reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{}
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition). In fact, a linear operation is completely positive if and only
if it has a Kraus representation~\cite{Kraus1983}. The minimum number of Kraus operators $K_i$ needed to represent the channel is called \textit{Kraus rank}. 
%
It can be seen from Kraus decomposition that quantum channels preserve
hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular in this work we use bases containing the so-called \textit{Pauli strings}, defined as 
\begin{equation}
\sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
\label{eq:pauli_strings}
\end{equation}
where $N$ is the number of two-level particles (\aka{} qubits), $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$, $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal in $\mcB(\hilbert)$. Also notice that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$. In particular, for one qubit systems, the
%
$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$
%
